Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-05-09 Paper/paper.tex

\begin{table*}
  \caption{AGN samples analysed in this work.}
  \label{tab:samples}
  \begin{tabular}{lcllrS}
    \hline
    Sample& $z$ range$^a$& Survey & Reference & Number & {Area} \\
    & & & & of quasars & {(deg$^2$)} \\
    \hline
    1 & 0.1--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
    2$^b$ & 0.4--2.2 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 2338 & 64.2 \\
    3$^b$ & 0.4--2.2 & --- NGP & \citet{2009MNRAS.392...19C} & 7027 & 127.7 \\
    4 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 \\
    5 & 3.7--4.7 & SDSS DR7 & \citet{2010AJ....139.2360S} & 1785 & 6248.0 \\
    6 & 3.6--5.2 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 \\
    7 & 3.8--5.3 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 \\
    8 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 \\
    9$^c$ & 4.7--5.5 & SDSS DR7 & \citet{2013ApJ...768..105M} & 103 & 6248.0 \\
    10 & 4.7--5.5 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 62 & 235.0 \\
    11 & 5.7--6.5 & SDSS Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 \\
    12 & 5.7--6.5 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 \\
    13 & 5.7--6.5 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 \\
    14 & 5.8--6.6 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 \\
    15 & 5.8--6.6 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 \\
    16 & 5.8--6.5 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 \\
    17$^d$ &4.0--6.5 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 \\
    18$^e$ & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 \\
    19$^e$ & 6.5--7.4 & UKIDSS & \citet{2015ApJ...801L..11V} & 1 & 3370.0 \\
    20$^e$ & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 \\
    \hline
  \end{tabular}\\
  \begin{minipage}{14.5cm}
    \textsuperscript{$a$}{Redshift range of the sample or, for small
      samples, approximate redshift range in which the survey is
      sensitive.}\\
    \textsuperscript{$b$}{Restricted to $z<2.2$.}\\
    \textsuperscript{$c$}{Restricted to $M_{1450}>-26.73$ quasars to
      avoid overlap with the \citet{2016ApJ...829...33Y} sample.}\\
    \textsuperscript{$d$}{Used only in Section~\ref{sec:global} and
      Appendix~\ref{sec:conv} due to lack of spectroscopic redshifts
      for majority of the sample.}\\
    \textsuperscript{$e$}{Used only in Section~\ref{sec:global} due to
      roughly estimated selection function.}
 \end{minipage}
\end{table*}

@@

%%GW: 2.5<z<2.6 QSOs are missing in this plot! Also, there are no open symbols for BOSS, but the numbers indicate that you excluded some in several redshift bins. The total numbers per redshift bin are not matching the number of BOSS QSOs.
\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
    % mosaic.py 
  \end{center}
  \caption{Homogenised quasar luminosity functions at $\lambda=1450$\,\AA\ in redshift bins from
    $z=0.1$ to $6.5$.  The symbols show our inferred binned
    luminosity functions from various data sets:
    \citet[red]{2010AJ....139.2360S},
    \citet[green]{2009MNRAS.392...19C},
    \citet[dark blue]{2013ApJ...773...14R},
    \citet[light blue]{2011ApJ...728L..26G},
    \citet[yellow]{2016ApJ...829...33Y},
    \citet[brown]{2013ApJ...768..105M},
    \citet[pink]{2016ApJ...833..222J},
    \citet[orange]{2010AJ....139..906W}, and
    \citet[grey]{2015ApJ...798...28K}.  Open circles in
    corresponding colours indicate excluded incomplete magnitude bins for
    the respective data sets. In each panel we give the number
    of considered quasars in the respective redshift bin,
    with the number in parentheses indicating the total number of quasars before
    excluding incomplete magnitude bins.
    In each redshift bin, the black
    curve shows the best-fit double power law model, which is
    represented by the median of the posterior probability
    distribution function.  The grey shaded area shows the
    one-sigma (68.26\%) uncertainty. 
    See Sections~\ref{sec:binnedlf} and \ref{sec:bins} for further
    details.}
  \label{fig:mosaic}
\end{figure*}

>>>>

\begin{table*}
  \caption{AGN samples analysed in this work.}
  \label{tab:samples}
  \begin{tabular}{lcllrS}
    \hline
    Sample& $z$ range$^a$& Survey & Reference & Number & {Area} \\
    & & & & of quasars & {(deg$^2$)} \\
    \hline
    1 & 0.0--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
    2$^b$ & 0.4--2.2 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 2338 & 64.2 \\
    3$^b$ & 0.4--2.2 & --- NGP & \citet{2009MNRAS.392...19C} & 7027 & 127.7 \\
    4 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 \\
    5 & 3.7--4.7 & SDSS DR7 & \citet{2010AJ....139.2360S} & 1785 & 6248.0 \\
    6 & 3.6--5.2 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 \\
    7 & 3.8--5.3 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 \\
    8 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 \\
    9$^c$ & 4.7--5.5 & SDSS DR7 & \citet{2013ApJ...768..105M} & 103 & 6248.0 \\
    10 & 4.7--5.5 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 62 & 235.0 \\
    11 & 5.7--6.5 & SDSS Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 \\
    12 & 5.7--6.5 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 \\
    13 & 5.7--6.5 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 \\
    14 & 5.8--6.6 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 \\
    15 & 5.8--6.6 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 \\
    16 & 5.8--6.5 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 \\
    17$^d$ &4.0--6.5 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 \\
    18$^e$ & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 \\
    19$^e$ & 6.5--7.4 & UKIDSS & \citet{2015ApJ...801L..11V} & 1 & 3370.0 \\
    20$^e$ & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 \\
    \hline
  \end{tabular}\\
  \begin{minipage}{14.5cm}
    \textsuperscript{$a$}{Redshift range of the sample or, for small
      samples, approximate redshift range in which the survey is
      sensitive.}\\
    \textsuperscript{$b$}{Restricted to $z<2.2$.}\\
    \textsuperscript{$c$}{Restricted to $M_{1450}>-26.73$ quasars to
      avoid overlap with the \citet{2016ApJ...829...33Y} sample.}\\
    \textsuperscript{$d$}{Used only in Section~\ref{sec:global} and
      Appendix~\ref{sec:conv} due to lack of spectroscopic redshifts
      for majority of the sample.}\\
    \textsuperscript{$e$}{Used only in Section~\ref{sec:global} due to
      roughly estimated selection function.}
 \end{minipage}
\end{table*}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
    % mosaic.py 
  \end{center}
  \caption{Homogenised quasar luminosity functions at
    $\lambda=1450$\,\AA\ in redshift bins from $z=0.1$ to $6.5$.  The
    symbols show our inferred binned luminosity functions from various
    data sets:
    \citet[red]{2010AJ....139.2360S},
    \citet[green]{2009MNRAS.392...19C},
    \citet[dark blue]{2013ApJ...773...14R},
    \citet[light blue]{2011ApJ...728L..26G},
    \citet[yellow]{2016ApJ...829...33Y},
    \citet[DR7 brown]{2013ApJ...768..105M},
    \citet[Stripe 82 teal]{2013ApJ...768..105M},
    \citet[pink]{2016ApJ...833..222J},
    \citet[orange]{2010AJ....139..906W}, and
    \citet[grey]{2015ApJ...798...28K}.
    Open circles in corresponding colours indicate magnitude bins
    excluded due to incompleteness for the respective data sets.  The
    number of AGN before this selection is shown in parentheses; the
    selected number of AGN is shown outside parentheses.  In each
    redshift bin, the black curve shows the best-fit double power law
    model, which is represented by the median of the posterior
    probability distribution function.  The grey shaded area shows the
    one-sigma (68.26\%) uncertainty.  See Sections~\ref{sec:binnedlf}
    and \ref{sec:bins} for further details.}
  \label{fig:mosaic}
\end{figure*}
